### 2011-12-16 docs/src/manual.tex

The conversion between Curry types and Haskell types,
i.e., the family of conversion operation \code{fromCurry}
and \code{toCurry}, is defined in the KiCS2 implementation
for all standard data types.
In particular, it is also defined on function types so that one can
easily implement external Curry I/O actions by using
Haskell I/O actions.
For instance, if we want to implement
an external operation to print some string as an output line,
we start by declaring the external operations in the Curry module \code{String}:
\begin{curry}
printString :: String -> IO ()
printString s = prim_printString $\$$## s

prim_printString :: String -> IO ()
prim_printString external
\end{curry}
Next we add the corresponding implementation in the file
\code{External_String.hs} (where \code{C_IO} and \code{OP_Unit} are the names
of the Haskell representation of the Curry type constructor \code{IO}
and the Curry data type \ccode{()}, respectively):
\begin{curry}
external_d_C_prim_printString :: CP.OP_List CP.C_Char -> ConstStore
                              -> CP.C_IO CP.OP_Unit
external_d_C_prim_printString s _ = toCurry putStrLn s
\end{curry}
Here, Haskell's I/O action \code{putStrLn} of type \ccode{String -> IO ()}
is transformed into a Curry I/O action \ccode{toCurry putStrLn}
which has the type
\begin{curry}
CP.OP_List CP.C_Char -> CP.C_IO CP.OP_Unit
\end{curry}
When we compile the Curry module \code{String},
KiCS2 combines these definitions in the target program so that
we can immediately use the externally defined operation
\code{printString} in Curry programs.

>>>>

In order to use Haskell I/O actions as an implementation
for external Curry I/O actions in an easy manner, the KiCS2 implementation
also provides a family of operations \code{fromHaskellIO$n$},
where $n$ denotes the number of parameters of the I/O action.
Each operation \code{fromHaskellIO$n$}
maps a Haskell I/O action into a Curry I/O action and performs
all data conversions for the arguments and result.
For instance, if we want to implement
an external operation to print some string as an output line,
we start by declaring the external operations in the Curry module \code{String}:
\begin{curry}
printString :: String -> IO ()
printString s = prim_printString $\$$## s

prim_printString :: String -> IO ()
prim_printString external
\end{curry}
Next we add the corresponding implementation in the file
\code{External_String.hs} (where \code{OP_Unit} is the name
of the Haskell representation of the Curry datatype \ccode{()}):
\begin{curry}
external_d_C_prim_printString :: CP.OP_List CP.C_Char -> ConstStore
                              -> CP.C_IO CP.OP_Unit
external_d_C_prim_printString s _ = fromHaskellIO1 putStrLn s
\end{curry}
When we compile the Curry module \code{String},
KiCS2 combines these definitions in the target program so that
we can immediately use the externally defined operation
\code{printString} in Curry programs.
